Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-26 docs/rmd/presentation/slides.tex
autogit

\begin{frame}{Statistical Test}
\protect\hypertarget{statistical-test}{}
\begin{table}

\caption{\label{tab:unnamed-chunk-5}Mean Error - P-Values (MWU)}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
  & tournament\_training\_errors & tournament\_testing\_errors & elexicase\_training\_errors & elexicase\_testing\_errors\\
\midrule
tournament\_training\_errors & 1.000 & 0.309 & 0.000 & 0.000\\
tournament\_testing\_errors & 0.309 & 1.000 & 0.002 & 0.000\\
elexicase\_training\_errors & 0.000 & 0.002 & 1.000 & 0.257\\
elexicase\_testing\_errors & 0.000 & 0.000 & 0.257 & 1.000\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

>>>>

\begin{frame}[fragile]{Statistical Test}
\protect\hypertarget{statistical-test}{}
\begin{verbatim}
##                            tournament_training_errors tournament_testing_errors
## tournament_training_errors               1.000000e+00              0.3092302963
## tournament_testing_errors                3.092303e-01              1.0000000000
## elexicase_training_errors                1.180222e-04              0.0024468832
## elexicase_testing_errors                 4.192079e-06              0.0001213887
##                            elexicase_training_errors elexicase_testing_errors
## tournament_training_errors              0.0001180222             4.192079e-06
## tournament_testing_errors               0.0024468832             1.213887e-04
## elexicase_training_errors               1.0000000000             2.567806e-01
## elexicase_testing_errors                0.2567805508             1.000000e+00
\end{verbatim}
\end{frame}
